\section{Grammatica}
\begin{itemize}
\item s   -\textgreater   layout  /

 \item layout   -\textgreater   import{\_}definition+	main{\_}group

 \item import{\_}definition   -\textgreater   IMPORT  FILE{\_}NAME  ;

 \item main{\_}group   -\textgreater   groups

 \item groups   -\textgreater   group{\_}preference*  
 
 (groups \textbar group{\_}definition)+

 \item group{\_}preference   -\textgreater   layout{\_}preference

 \item group{\_}preference   -\textgreater   margin{\_}preference

 \item group{\_}preference   -\textgreater   collapse{\_}preference

 \item group{\_}preference   -\textgreater   args{\_}preference

 \item group{\_}definition   -\textgreater   [  (CLASS{\_}TYPE   
 
 \textbar   CLASS{\_}NAME{\_}WITH{\_}PACKAGE   \textbar   CLASS{\_}NAME   
 
 \textbar   CLASS{\_}RANGE{\_}WITH{\_}PACKAGE)  ]

 \item layout{\_}preference   -\textgreater   LAYOUT  LAYOUT{\_}CARD

 \item collapse{\_}preference   -\textgreater   COLLAPSE  COLLAPSE{\_}TYPE

 \item args{\_}preference  HIDE{\_}ARGS

 \item margin{\_}preference   -\textgreater   MARGIN  MARGIN{\_}SIZE{\_}TOP  
 
 MARGIN{\_}SIZE{\_}RIGHT  MARGIN{\_}SIZE{\_}BOTTOM  MARGIN{\_}SIZE{\_}LEFT

 \item model   -\textgreater   (class{\_}definition+   \textbar   package{\_}definition+)  /

 \item package{\_}definition   -\textgreater   PACKAGE  PACKAGE{\_}NAME  \{  class{\_}definition+  \}

 \item class{\_}definition   -\textgreater   COMMENT?  VISIBILITY?  
 
 CLASS{\_}TYPE  CLASS{\_}NAME  \{  relations?  attributes?  methods?  \}

 \item relations   -\textgreater   RELATIONS  \{  relation  \}

 \item relation   -\textgreater   COMMENT?  RELATION{\_}TYPE  
 
 (RELATION{\_}CLASS{\_}NAME 
 
 \textbar RELATION{\_}CLASS{\_}NAME{\_}WITH{\_}PACKAGE)  relation{\_}cardinality?  
 
 (RELATION{\_}COMMA  (RELATION{\_}CLASS{\_}NAME 
 
 \textbar RELATION{\_}CLASS{\_}NAME{\_}WITH{\_}PACKAGE)  
 
 relation{\_}cardinality?)*  RELATION{\_}END

 \item relation{\_}cardinality   -\textgreater   CARDINALITY{\_}START  CARDINALITY  
 
 RELATION{\_}CARDINALITY{\_}COMMA   CARDINALITY 
 
 RELATION{\_}CARDINALITY{\_}COMMA  CARDINALITY  CARDINALITY{\_}STOP

 \item attributes   -\textgreater   ATTRIBUTES  \{  attribute+  \}

 \item attribute   -\textgreater   COMMENT?  VISIBILITY?  
 
 (typed{\_}attribute{\_}name \textbar attribute{\_}name)  default{\_}value?

 \item attribute{\_}name   -\textgreater   VARIABLE

 \item typed{\_}attribute{\_}name   -\textgreater   VARIABLE  VARIABLE

 \item default{\_}value   -\textgreater   EQUAL  equal{\_}to

 \item equal{\_}to   -\textgreater   (NUMBER \textbar STRING)

 \item methods   -\textgreater   METHOD  \{  method  \}

 \item method   -\textgreater   COMMENT?  VISIBILITY?  
 
 (typed{\_}method \textbar method{\_}name)  
 
 "("  (method{\_}arg  (,  method{\_}arg)*)?  ")"  ;

 \item typed{\_}method   -\textgreater   VARIABLE  VARIABLE

 \item method{\_}name   -\textgreater   VARIABLE

 \item method{\_}arg   -\textgreater   COMMENT?  (typed{\_}argument 
 
 \textbar argument)  default{\_}value?

 \item argument   -\textgreater   VARIABLE

 \item typed{\_}argument   -\textgreater   VARIABLE  VARIABLE

 \item attribute{\_}type   -\textgreater   type

 \item type   -\textgreater   VARIABLE

 \end{itemize}